---
title: "13-07-2021"
author: "Chanya"
date: "7/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages, warning=TRUE, include=FALSE}
if(!require(pacman))install.packages("pacman")

pacman::p_load('tidyverse',  'gapminder',
               'forcats', 'scales')
```

```{r data, include=FALSE}
scoobydoo <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-07-13/scoobydoo.csv')
```

# Quick overview 
```{r}
library(skimr)
skim(scoobydoo)
```
## Will explore...
1. Top-rated episodes from IMDB? 
2. Who caught the most?
3. Most common motive? 

### Transforming data
https://www.geeksforgeeks.org/how-to-convert-dataframe-column-from-character-to-numeric-in-r/

```{r}
scoobydoo <- scoobydoo %>% 
  select(series_name:date_aired, starts_with("caught_"), starts_with("setting_"), motive)
scoobydoo <- transform(scoobydoo,
                             imdb = as.numeric(imdb),engagement = as.numeric(engagement), caught_fred = as.logical(caught_fred), caught_daphnie = as.logical(caught_daphnie), caught_velma = as.logical(caught_velma), caught_shaggy = as.logical(caught_shaggy), caught_scooby = as.logical(caught_scooby), setting_terrain = as.factor(setting_terrain), setting_country_state = as.factor(setting_country_state), motive = as.factor(motive))
sapply(scoobydoo, class)
```

### Top-rated episodes 
```{r}
hist(scoobydoo$imdb)
skim(scoobydoo$imdb)
```

Find the series that have scores above 75th percentile (7.7)

```{r}
top <- scoobydoo %>%
  filter(imdb >= 7.7) %>%
  arrange(desc(imdb))
head(top, 10)
```
```{r}
ggplot(top, aes(x=series_name,y=imdb, color=series_name)) +
  geom_point() +
  coord_flip() +
  labs(title="Top-rated Scoobydoo series according to IMDB scores",subtitle="no. of dots = no. of episodes under specific series") +
  theme(legend.position = "none",plot.title = element_text(lineheight=.8, face="bold",hjust=3))
ggsave("imdb.png")
```
According to the plot, I would recommend Supernatural movie and Scooby-Doo Mystery Incorporated series to someone new to Scoobydoo! 

### Who caught the most? 
According to the data, who contribute the most to the number of catch? 
https://intellipaat.com/community/5004/how-to-count-true-values-in-r
https://stackoverflow.com/questions/6778908/transpose-a-data-frame
https://www.geeksforgeeks.org/change-column-name-of-a-given-dataframe-in-r/
https://www.dummies.com/programming/r/how-to-create-a-data-frame-from-a-matrix-in-r/
```{r}
caught <- scoobydoo %>%
  summarize(
    fred = length(caught_fred[caught_fred == TRUE]), 
    daphnie = length(caught_daphnie[caught_daphnie == TRUE]),
    velma = length(caught_velma[caught_velma == TRUE]),
    shaggy = length(caught_shaggy[caught_shaggy == TRUE]),
    scooby = length(caught_scooby[caught_scooby == TRUE]),
    other = length(caught_other[caught_other == TRUE])
  )
## Transpose and change column name 
caught <- t(caught)
caught <-  as.data.frame(caught)
class(caught)
caught <- rownames_to_column(caught, var = "name") %>% as_tibble()
colnames(caught) <- c("name","number")
head(caught)
```
https://bbc.github.io/rcookbook/#do_something_else_entirely
```{r}
caught_plot <- ggplot(caught, aes(x = reorder(name, number), y = number)) +
  geom_bar(stat="identity", position="identity", fill="#1380A1") +
  geom_hline(yintercept = 0, size = 1, colour="#333333") +
  coord_flip() +
  labs(title="Who caught the most?") +
  theme(panel.grid.major.x = element_line(color="#cbcbcb"), 
        panel.grid.major.y=element_blank(),plot.title = element_text(lineheight=.8, face="bold"),axis.title.y = element_blank())
caught_plot
ggsave("caught.png")
```

### Most common motive 
```{r}
motive <- scoobydoo %>%
  count(motive)
```

```{r}
motive_plot <- ggplot(motive, aes(x=reorder(motive,n), y=n)) +
  geom_bar(stat="identity",fill="plum3") +
  coord_flip() +
  labs(title="What is the most common motive?") +
  theme(panel.grid.major.x = element_line(color="#cbcbcb"), 
        panel.grid.major.y=element_blank(),plot.title = element_text(lineheight=.8, face="bold"),axis.title.y = element_blank())
ggsave("motive.png")
```

### Data Source 
https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-07-13/readme.md
