---
title: "27-07-2021"
author: "Chanya"
date: "8/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages, echo=TRUE, warning=TRUE}
if(!require(pacman))install.packages("pacman")
pacman::p_load('tidyverse',  'gapminder',
               'forcats', 'scales','plotly')
```

```{r read in dataset, message=FALSE, warning=FALSE}
olympics <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-07-27/olympics.csv')
```

## History of Olympic Games
https://www.scholastic.com/teachers/articles/teaching-content/history-olympic-games/

## Badminton 
Recently, I enjoy watching the Olympic Games Tokyo 2020, and I am most addicted to badminton games. Therefore, I am interested in how this sport has evolved over time and which country has won the most medals. 

#### Q) Which country won the most badminton medals? 
```{r message=FALSE, warning=FALSE}
badminton <- olympics %>%
  filter(sport=="Badminton", medal != "NA") %>%
  group_by(noc,medal) %>%
  summarise(
    number = length(medal)
  ) 
view(badminton)

# order Team by total medal count
# https://www.kaggle.com/heesoo37/olympic-history-data-a-thorough-analysis/report
levs_badminton <- badminton %>%
  group_by(noc) %>%
  summarize(Total=sum(number)) %>%
  arrange(Total) %>%
  select(noc)
badminton$noc <- factor(badminton$noc, levels=levs_badminton$noc)
# https://www.stat.berkeley.edu/~s133/factors.html
badminton$medal <- factor(badminton$medal, labels=c("Gold","Silver","Bronze"))
```
```{r message=FALSE, warning=FALSE}
ggplot(badminton, aes(x=noc,y=number,fill=medal)) +
  geom_col() +
  theme_bw() +
  coord_flip() + 
  scale_fill_manual(values=c("#D6AF36","#D7D7D7","#A77044")) +
  xlab("") +
  ylab("") +
  ggtitle("China won most Badminton medals in the Olympic history") +
  labs(caption="source:www.sports-reference.com")
  theme(plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(colour = "#D3D3D3"),
        panel.grid.minor = element_line(colour = NULL),
        text=element_text(size=14,  family="Gill Sans"))
ggsave("Badminton.png")
```

#### Creating a map for countries with most badminton champions 
https://www.kaggle.com/heesoo37/olympic-history-data-a-thorough-analysis/report
```{r message=FALSE, warning=FALSE}
# Load data file matching NOCs with mao regions (countries)
# https://raw.githubusercontent.com/rgriff23/Olympic_history/master/data/noc_regions.csv
noc <- read_csv("https://raw.githubusercontent.com/rgriff23/Olympic_history/master/data/noc_regions.csv")
# raname column from NOC to noc
# http://www.cookbook-r.com/Manipulating_data/Renaming_columns_in_a_data_frame/
names(noc)[1] <- "noc"
# Add regions to data and remove missing points
data_regions <- badminton %>% 
  left_join(noc,by="noc") %>%
  filter(!is.na(region))
```

```{r message=FALSE, warning=FALSE}
total_badminton <- data_regions %>%
  group_by(region) %>%
  summarize(total = sum(number)) %>%
  arrange(desc(total))
```

Data for mapping
```{r}
world <- map_data("world")
mapdat <- tibble(region=unique(world$region))
mapdat <- mapdat %>% 
  left_join(total_badminton, by="region")
mapdat$total[is.na(mapdat$total)] <- 0
world <- left_join(world, mapdat, by="region")
```

Plotting 
```{r message=FALSE, warning=FALSE}
badminton_map <- ggplot(world, aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = total)) +
  labs(title = "Most badminton medalists come from Asia",
       caption="source:www.sports-reference.com",
       x = NULL, y=NULL) +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        panel.background = element_rect(fill = "white"),
        plot.title = element_text(hjust = 0.5),
        text=element_text(family="Gill Sans"),
        legend.position="top") +
  guides(fill=guide_colourbar(title="total medals")) +
  scale_fill_gradient(low="grey",high="red")
```

Most countries seem to be located on the East. 

```{r}
#install and load in ggforce for facet zoom
library(ggforce)
```

Zoom in...
```{r echo=TRUE}
badminton_map +
  facet_zoom(xlim = c(70, 140)) 
ggsave("badminton_zoom.png")
```

#### Q) Gold medal distribution across time (1992-2016)
```{r}
summer <- olympics %>%
  select(noc,games:medal) %>%
  filter(sport=="Badminton", medal == "Gold") %>%
  arrange(year) %>%
  group_by(year,event,medal,noc) %>%
  count()
```

```{r}
ggplot(summer, aes(x=year,fill=noc)) +
  geom_bar() +
  theme_classic() +
  labs(title="Only these six countries could take badminton gold medals home",subtitle="gold medal distribution across 5 events from 1992 to 2016", caption="source:www.sports-reference.com",y=NULL) +
  scale_x_continuous(name ="year",breaks=unique(summer$year)) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 1),
        text=element_text(family="Gill Sans"),
        legend.position="top",
        legend.title = element_blank()) +
  guides(colour = guide_legend(nrow = 1))
ggsave("gold.png")
```

#### Special thanks to the below sources on how to beautify plots
* http://www.sthda.com/english/wiki/ggplot2-axis-ticks-a-guide-to-customize-tick-marks-and-labels#change-axis-lines
* http://www.sthda.com/english/wiki/ggplot2-colors-how-to-change-colors-automatically-and-manually#use-rcolorbrewer-palettes
* http://www.sthda.com/english/wiki/ggplot2-legend-easy-steps-to-change-the-position-and-the-appearance-of-a-graph-legend-in-r-software
* https://towardsdatascience.com/how-to-make-stunning-bar-charts-in-r-a-complete-guide-with-ggplot2-c8f3b87de4d1

#### Source
* https://www.kaggle.com/heesoo37/olympic-history-data-a-thorough-analysis/report
* https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-07-27/readme.md

